A Formal Model of Checked C

### 2023-01-10 sandp23/introduction.tex
[review] fix typo

\begin{itemize}
\item~\umode \emph{region} or~\emph{tainted region} (low privilege tainted region): This partition contains tainted types (\ie functions and pointers) and can only access tainted pointers.
\item~\cmode \emph{region} or~\emph{safe region} (high privilege untainted or checked region): This partition contains the remaining (untainted) code and data and has complete access to~\cmode region.
The functions in~\cregion can invoke any function in~\ucregion and access all its data but not the other way around, except for call-back functions, which we will discuss later.
\end{itemize}
% 
\mz{                            %
  This paragraph is unclear. 
  % 
  How does regions look like? Can one region nested in another?
  %
  If not, ``This partition contains the remaining (untainted) code and data and
  has complete access to~\cmode region.'' creates a sense of recursive
  definition of \cregion.
}\lc{<- same question, maybe giving an abstract example?}
%

>>>>

\begin{itemize}
\item~\umode \emph{region} or~\emph{tainted region} (low privilege tainted region): This partition contains tainted types (\ie functions and pointers) and can only access tainted pointers.
\item~\cmode \emph{region} or~\emph{safe region} (high privilege untainted or checked region): This partition contains the remaining (untainted) code and data and has complete access to~\cmode region.
The functions in~\cregion can invoke any function in~\ucregion and access all its data but not the other way around, except for call-back functions, which we will discuss later.
\end{itemize}
% 
\mz{                            %
  This paragraph is unclear. 
  % 
  What do regions look like? Can one region be nested in another?
  %
  ``This partition contains the remaining (untainted) code and data and
  has complete access to~\cmode region.'' creates a sense of recursive
  definition of \cregion.
}\lc{<- same question, maybe giving an abstract example?}
%
